\begin{textsample}{NEG Dim 3 – profiled\_gpt – Score -2.00 – profiled\_gpt/t000124\_gpt.txt}  \label{ex:f3_neg_004}
well I know they 're going to have a go at me about it, that ’s a given, but I ’m not really bothered in that \textbf{sense}, because I can just sit them down and say look, this is why I ’m \textbf{changing} direction.
I can explain that I ’m in this sort of in‑between phase at the \textbf{moment}, where I ’m moving away from what I was doing and edging towards creating something different.
It ’s not that I ’m claiming to have invented something totally original, it ’s that for me it ’s new, and I ’m learning a whole load of things I didn't know before.
I ’d talk them through that : that I ’m deliberately going out and learning from people who are already doing what I want to be doing.
I ’m watching what they do, listening to how they talk about it, and trying to \textbf{pick} up as much as I can from them.
That ’s a big part of it for me, that \textbf{sense} of actually studying people who are already there rather than just sitting around talking about what I might do one day.
And I ’d say to them that in this kind of entrepreneurial stuff there are these common themes that run through everyone ’s story – you know, taking a risk, \textbf{changing} tack, learning on the job – but at the same time everyone ’s path is quite individual.
So I ’m not trying to copy someone else ’s life, I ’m trying to understand the patterns and then find my own route through it.
Even if they don't really get where I ’m coming from, or they can't see the bigger picture I ’ve got in my head, there ’s still value in what I ’m doing.
I ’d stress that.
I ’m learning from other people who are doing it already, and that in itself is worthwhile.
They might roll their eyes or think I ’ve gone a bit mad, but I can at least lay out the logic : I ’m \textbf{changing} direction, I ’m in a transition, I ’m learning from people ahead of me, and I ’m trying to build something different for myself.
Whether they fully understand it or not, that ’s what I ’ll be doing.

% matched lemmas: change, moment, pick, sense
\end{textsample}
