\begin{textsample}{POS Dim 1 – unprofiled\_gpt – Score 6.00 – unprofiled\_gpt/t001038\_gpt.txt}  \label{ex:f1_pos_028}
I actually see you as someone who is really evolving, you know.
People aren't fixed ; we ’re dynamic and we \textbf{change} on all sorts of levels as we go through life – physically, psychologically, spiritually, emotionally.
You ’re not the same person you were a few years ago, and you won't be the same a few years from now, and that ’s not a problem, that ’s kind of the point.
It feels like right now you ’re at a really major crossroads.
On one side there ’s “ business as usual, ” just carrying on the \textbf{way} things have always been.
On the other side there ’s this much wider, \textbf{more} open path where you get to redefine things, where you ’re not just repeating old patterns but really choosing what suits you now.
And I think this is exactly the \textbf{moment} to be really assertive about who you are and what you want.
If going to bed at ten feels right for you, then \textbf{own} that.
Be proud of that choice instead of apologising for it or feeling like you have to justify it.
There ’s nothing wrong with being the “ strange sober person ” who likes early nights.
Stop putting yourself down for those things.
They ’re not weaknesses, they ’re just part of who you are \textbf{becoming}.
The \textbf{more} you stand in that and say, “ Yes, this is me, ” the \textbf{more} solid you ’ll feel in this new phase, and the easier it will be to walk that wider path instead of slipping back into the old one.

% matched lemmas: become, change, moment, more, own, way
\end{textsample}
