\begin{textsample}{POS Dim 1 – profiled\_gpt – Score 5.00 – profiled\_gpt/t000937\_gpt.txt}  \label{ex:f1_pos_009}
I think to really get the story going we ’d have to step back from just “ academic integrity ” and talk about integrity \textbf{more} broadly.
If we frame it as integrity in general – how people act with integrity, how they teach it, how they deal with grey areas – it opens things up and makes it \textbf{more} interesting and relevant to \textbf{more} people.
We ’d also need to phrase it in a \textbf{way} that actively encourages people to invite others to be interviewed.
So instead of it just being us approaching individuals, it \textbf{becomes}, “ Who else do you know who ’s grappled with this? ” That \textbf{way}, each person feels they can nominate colleagues or friends, and the story naturally spreads through those invitations.
I ’d want to link it to a really concrete problem as well, something that ’s already worrying people, like students using ghost writers.
If we ’re explicit about that sort of issue – not skirting around it but actually naming it – then people have something solid to respond to.
Talking openly about those kinds of problems can actually be a \textbf{way} of generating solutions, because everyone brings their \textbf{own} experiences and \textbf{ideas}.
So the overall theme would be framed around integrity, but grounded in these specific, real-world problems.
That combination – broad principle plus concrete cases – would help people see why it matters and what they can contribute, and it would give the whole project a \textbf{clear} narrative thread.

% matched lemmas: become, clear, idea, more, own, way
\end{textsample}
