\begin{textsample}{POS Dim 1 – profiled\_gpt – Score -1.00 – profiled\_gpt/t000435\_gpt.txt}  \label{ex:f1_pos_035}
well they 've been on about doing the A14 for years and years, and every time it gets anywhere near actually happening someone kicks off about it and it all gets pushed back again.
And it ’s not even in massively built‑up bits, it ’s little villages and fairly empty stretches where people still manage to mount enough of a protest to stall it.
Thing is, you wouldn't need anything that radical to make a big difference.
If you just took out all those awful at‑grade junctions and turned them into proper grade‑separated ones, that alone would sort a lot of the congestion and safety issues.
It ’s not rocket science, it ’s just a case of actually doing it.
But I can't see them getting it through without dangling some extra money in front of people somehow, and that ’s where I think they ’ll end up going down the private route.
Some company brought in to pay for it, run it, maintain it, probably on one of those PFI‑type deals where they get their money back over twenty, thirty years.
That way the government can say, oh look, it ’s not coming straight out of the public purse.
And knowing my lot, it ’ll probably be someone in our office who sits down and works out how to make the numbers stack up, how you structure the contract so it all looks palatable.
So we ’ll all moan about it over dinner and then go into work on Monday and help them figure out how to do it.

% matched lemmas: 
\end{textsample}
