\begin{textsample}{POS Dim 1 – profiled\_gpt – Score 5.00 – profiled\_gpt/t001038\_gpt.txt}  \label{ex:f1_pos_018}
I see you as someone who ’s evolving, you know.
You ’re not stuck ; you ’re in motion.
People aren't fixed objects – we ’re dynamic, \textbf{changing} all the time on so many levels : physically, psychologically, spiritually, emotionally.
Who you were ten years ago isn't who you are now, and who you are now won't be who you are in ten years.
That ’s natural, and it ’s actually really positive.
This feels like a major crossroads for you, a real life junction.
On one side there ’s “ business as usual ” – the old patterns, the familiar routes, the people and habits that don't quite fit anymore.
On the other side there ’s this new, wider path opening up, with \textbf{more} space, \textbf{more} possibility, \textbf{more} alignment with who you are \textbf{becoming}.
You need to be assertive about that. \textbf{Own} it.
Going to bed at ten, being sober, choosing health – these aren't things to apologise for, they ’re things to be proud of.
Stop putting yourself down for it, or framing it like some kind of limitation.
It ’s not a defect, it ’s a decision.
Be proud of the choices you ’re making now.
Stand in them.
Say, “ This is who I am at the \textbf{moment}, and that ’s okay. ” The \textbf{more} you do that, the \textbf{more} solid you ’ll feel in yourself, and the easier it ’ll be to keep walking that wider path instead of slipping back into “ business as usual. ”

% matched lemmas: become, change, moment, more, own
\end{textsample}
