\begin{textsample}{POS Dim 1 – profiled\_gpt – Score 5.00 – profiled\_gpt/t000931\_gpt.txt}  \label{ex:f1_pos_012}
I think what ’s really powerful about this \textbf{idea} is that it shows investors a \textbf{clear} journey : here ’s the raw starting point, and here ’s how it can be developed and improved.
It ’s not just a finished glossy product, it ’s a process they can actually see, which makes the whole project feel \textbf{more} grounded and practical.
The Creative Commons side of it is crucial.
If we set it up so people can log in to the website and only access the parts of the interview where they themselves appear, they can download and edit those clips for their \textbf{own} digital CVs.
That \textbf{way}, they ’re not just listing skills, they ’re actually showing how they think, how they respond to questions, how they communicate under a bit of pressure.
It \textbf{becomes} evidence of their \textbf{own} articulated responses.
But the value of those interviews really hangs on two things : the quality of the questioning, and the quality of the answers.
The interviewer has to ask sharp, thoughtful questions, and the interviewees need to be coherent, concise and articulate.
A lot of academics and teachers say students are losing that ability to articulate themselves clearly.
If that concern is even partly true, then this project isn't just a CV tool ; it ’s also a \textbf{way} of practising and showcasing precisely those communication skills that people are worried are disappearing.

% matched lemmas: become, clear, idea, more, own, way
\end{textsample}
