\begin{textsample}{POS Dim 3 – profiled\_gpt – Score 2.00 – profiled\_gpt/t001107\_gpt.txt}  \label{ex:f3_pos_019}
We got in really late and honestly, when we first arrived I thought we ’d made a \textbf{massive} mistake.
Our street looked so rough – loads of vandalism, graffiti everywhere, it just felt a bit dodgy.
But then in the daytime it was actually really nice, totally different vibe, so that was a bit of a relief.
The annoying thing with Barcelona is everything ’s so spread out.
All the main sights are miles apart, so we ended up walking absolutely everywhere.
We could ’ve done the tour buses or figured out the public transport, but because it was such a short trip we just hadn't really researched anything properly.
Compared to Paris, where all the big attractions are quite close together, it did feel a bit of a faff.
We did a ridiculous amount of walking.
I didn't really mind, but the others aren't used to that much, so they were flagging a bit.
The first day was still really nice though.
We just wandered around and stumbled across this festival thing, which was really fun.
In the evening we went to this \textbf{massive} light and fountain exhibition.
It ’s at this gorgeous building that ’s now the national museum – it looks like it used to be a palace or stately home, up on a hill with fountains and big sweeping steps.
At the bottom there ’s this \textbf{huge} fountain and they do a music and water display.
That was miles away too, so more walking.
And because I was the one who ’d vaguely suggested it, I somehow ended up in charge of directions, even though I ’d never been there before.
We did see the Sagrada Família and that was incredible – you walk in and just go “ wow ”.
The city ’s definitely worth going to, even if it ’s not as pretty as some others I ’ve been to.
The beach was actually fine as well, despite what people say.

% matched lemmas: huge, massive
\end{textsample}
