\begin{textsample}{NEG Dim 1 – profiled\_gpt – Score -5.00 – profiled\_gpt/t000334\_gpt.txt}  \label{ex:f1_neg_008}
well I I think a lot of what you ’ve been saying is right, really.
It does feel as if those natural freedoms we took for granted are being chipped away bit by bit.
You see it everywhere now – all this surveillance, all the government snooping, and it ’s not just here.
The Americans are at it, we ’re at it in the UK, and then there ’s the whole business with CCTV cameras on every corner.
You can't move without feeling you ’re being watched or recorded by somebody, somewhere.
At the \textbf{same} time, though, for all that, we ’re still relatively lucky compared with some parts of the world.
If you look at somewhere like China, for instance, the level of control there is on a completely different scale.
They don't just watch you, they really clamp down on what people can actually do in public.
You can't just have a big public gathering there in the way you could here ; they ’re very tightly restricted, monitored, broken up if they ’re not approved.
The state keeps such a firm grip on people ’s movements and on any sign of dissent.
What makes it interesting, and a bit unpredictable, is that in China people ’s expectations of freedom are starting to rise.
As more people see what life is like elsewhere, and as they become more aware, they begin to want more say, more space to \textbf{speak} and to assemble.
That sort of rising expectation can't be bottled up forever.
It ’s the kind of thing that, over time, can lead to \textbf{real} upheaval – even revolution – if it goes on long enough without any outlet.
But at the \textbf{moment}, the government there still has extremely tight control.
They ’ve built a whole system designed to keep a lid on those pressures – surveillance, restrictions on gatherings, all of that.
So you ’ve got this tension : on the one hand, a population whose \textbf{sense} of what freedom ought to look like is slowly expanding, and on the other, a state that ’s determined to keep \textbf{everything} firmly in hand.
How that plays out in the long run is hard to say, but it does underline how, for all our complaints about being watched here, there are places where the screws are turned much harder.

% matched lemmas: everything, moment, real, same, sense, speak
\end{textsample}
