\begin{textsample}{NEG Dim 1 – profiled\_gpt – Score -5.00 – profiled\_gpt/t001651\_gpt.txt}  \label{ex:f1_neg_006}
well over that eighteen \textbf{months} or so I was back and forth to the GP a lot because of this persistent spotting and the fact that I was putting on weight.
I kept saying, “ I ’m still bleeding, this is still going on, ” and it just \textbf{carried} on and on.
In that time they did pick up that I had an underactive thyroid and high blood pressure, so I was diagnosed and treated for both of those.
The thyroid in particular became the sort of explanation for \textbf{everything}.
Each time I went I would say that the bleeding hadn't stopped, that I was still spotting, and it was becoming a constant thing rather than something that came and went.
But the doctor kept attributing the bleeding to the thyroid problem, as if that neatly wrapped it all up.
I was being medicated for the thyroid and the blood pressure, and there was this \textbf{sense} that once those were under control \textbf{everything} else would sort itself out, even though I was saying quite clearly that the bleeding was continuing.
This went on for about eighteen \textbf{months}.
It wasn't as if I went once or twice ; I was repeatedly going back, reporting the \textbf{same} symptoms, and it was still put down to the thyroid.
The weight gain and the tiredness fitted that picture, so the bleeding was just folded into it.
Eventually, though, I was referred to a gynaecologist.
Once I got to the gynaecologist things moved very quickly.
He did a very simple procedure – just a scrape of the lining of the womb – \textbf{nothing} elaborate, something that was low-cost and straightforward.
There was no big build-up to it, it was just done as a matter of course.
On the strength of that little scrape, I was called back to the hospital the \textbf{same} day.
That was when they told me it was endometrial cancer.
So after all those \textbf{months} of being told it was the thyroid and being treated for that, it turned out that a very basic test on the uterine lining was what finally revealed what was really going on.

% matched lemmas: carry, everything, month, nothing, same, sense
\end{textsample}
