\begin{textsample}{NEG Dim 1 – unprofiled\_gpt – Score -6.00 – unprofiled\_gpt/t000434\_gpt.txt}  \label{ex:f1_neg_023}
No, what gets me is that now it feels like the tiniest bit of snow is just an excuse for people not to go to work.
Any little flurry and suddenly \textbf{everything} grinds to a halt and everyone ’s got a reason they “ can't possibly ” get in.
It ’s like the default reaction is, “ Oh well, that ’s it then, can't be \textbf{expected} to do anything, ” rather than even \textbf{trying}.
I mean, I remember one time when it was really bad – proper snow, not just a dusting.
I actually got in the car and drove all the way from here up to the office.
It was a long drive, took ages, roads were awful, but I thought, you know, you make the effort, you get there.
And when I finally arrived, hardly anyone who actually lived near the office had \textbf{bothered} to turn up.
They were all at home, even though they were just down the road.
I ’d come miles in the snow, and the people who could practically walk it just didn't.
That really annoyed me – I ’d done the slog, and they just used the weather as a get‑out.
And that wasn't even the worst I ’ve seen.
Years before that, there was this time when the roads just weren't gritted at all. \textbf{Nothing}.
They knew the snow was coming, everyone did, but they didn't prepare properly.
So when it hit, \textbf{everything} just collapsed.
I remember the M11 being completely jammed – people \textbf{stuck} there for hours and hours, some of them up to twenty‑four hours.
Literally a whole day on the motorway, going nowhere, because it hadn't been gritted and \textbf{everything} seized up.
That ’s the thing : it wasn't as if the bad weather came out of nowhere.
They had warning, they knew it was on the way, and still they didn't get the roads sorted in time.
No grit down, no proper preparation, and then you ’ve got all these people stranded.
It was a complete failure to plan for something they could see coming.
So on the one hand you ’ve got people who ’ll grab any bit of snow as a reason to stay home, and on the other hand you ’ve got the authorities who don't \textbf{seem} to take it seriously until it ’s too late.
When it ’s genuinely bad, like those times I ’m talking about, fair enough – it really does disrupt \textbf{everything}.
But that ’s exactly when you need the roads treated properly and some effort from everyone, not this combination of “ can't be \textbf{bothered} ” and “ didn't prepare. ”

% matched lemmas: bother, everything, expect, nothing, seem, stick, try
\end{textsample}
