\begin{textsample}{NEG Dim 1 – profiled\_gpt – Score -5.00 – profiled\_gpt/t001187\_gpt.txt}  \label{ex:f1_neg_002}
So there we are, absolutely soaked, mud everywhere, and we don't know a soul.
I ’m just \textbf{trying} to get this Year Nine lad registered for his cross-country.
I keep going up to different people with clipboards, asking where I ’m supposed to sign him in.
Every time they ’re checking their lists, and his name ’s not there, his school ’s not there, \textbf{nothing}.
Properly awkward.
Eventually one of them says, “ Oh yes, it ’s fine, he ’s in the one o’clock race, just come back about quarter past two, ” so I think, right, at \textbf{least} we ’re sorted.
Because it ’s chucking it down and the mud is ridiculous, we decide not to \textbf{bother} walking the course like everyone else \textbf{seems} to be doing.
Instead I go back, move the car a bit closer so we don't have to trek miles in that weather.
We head back to the tents later on to collect his race bib, \textbf{expecting} it all to be straightforward now.
I give them his details again and they look down the list and say, “ No, his school ’s not on here. ” And I ’m thinking, we ’ve already done this, we ’ve already been told he ’s in the race.
Then it turns out we ’re at the wrong team ’s tent altogether.
We ’ve been standing there, in the rain, talking to the wrong people.
So all that faffing about, all that trudging through the mud, and we ’re not even in the right place.
At that point I ’m just \textbf{trying} to get him to the correct tent and sorted, but it ’s all a bit of a farce, really.

% matched lemmas: bother, expect, least, nothing, seem, try
\end{textsample}
