\begin{textsample}{NEG Dim 5 – unprofiled\_gpt – Score -2.00 – unprofiled\_gpt/t000168\_gpt.txt}  \label{ex:f5_neg_024}
yeah I think you 're right, it really *should* be a small one, not just because it 's for kids but because not all grown‑ups are as fit as me either.
I was thinking about my friend who writes horror stories – you know, she ’s really not fit at all – and I could really imagine her doing the relaxed, kiddy version.
And actually, there were people today who were clearly not super‑fit : there were older people, and even people just walking it rather than running.
It made me think how nice it is that there ’s a version where you can just take your time, splash through the mud, climb a few things, and not feel like you have to be some kind of super‑athlete.
A really gentle, child‑friendly one would be perfect for people like that, and for kids, and for nervous grown‑ups too.
I was really nervous before mine, remember?
I kept thinking, “ What if I can't do it?
What if I ’m not strong enough? ” But once I got going, I realised I ’m actually much stronger than I thought.
I \textbf{managed} all those muddy bits and all the climbing and crawling, and I did it all on my own.
That feeling of “ oh, I *can* do this ” was amazing.
Because of that, now I feel like maybe I could try something a bit more difficult.
That ’s why I ’ve started thinking about doing a Spartan Race.
The obstacles in that are properly scary – they look really intimidating in the photos – but having got through this one, I ’m \textbf{thinking}, “ well, maybe I *can* \textbf{manage} the next step up. ” So doing this relaxed, muddy race, and seeing how it can work for kids and for people who aren't very fit, has actually made me feel brave enough to try something much tougher.
It ’s funny how a friendly, easy version can give you the confidence to take on a big, scary Spartan Race afterwards.

% matched lemmas: manage, thinking
\end{textsample}
