\begin{textsample}{NEG Dim 2 – unprofiled\_gpt – Score -3.00 – unprofiled\_gpt/t000657\_gpt.txt}  \label{ex:f2_neg_027}
so yeah after I went back on the server I ’d actually had this idea in my head for ages about doing this \textbf{massive} tower project, like properly \textbf{huge}, and that was going to be my \textbf{big} thing.
But then I started thinking it ’d be more fun if it wasn't just me doing my own giant monument, so instead of just going ahead with the tower I started setting these little challenges for everyone. so rather than “ here ’s my \textbf{big} tower, look at it, ” it was more like “ right, here ’s a task, here ’s a theme, let ’s see what you can come up with, ” and that made it feel a lot more collaborative. everyone could chip in and we ’d all be working around the same area, bouncing off each other ’s ideas while we were \textbf{building}. then, while we were in the middle of \textbf{building} this \textbf{big} thing together, we had this one guy on the server who was supposed to be the expert with TNT, you know, like he knew how to use it properly. and he ended up blowing up the walls by accident, and the whole place just got completely flooded. it basically wrecked what we were doing. so at that point I asked if we could have creative mode just so we could fix it all, rebuild the walls, get the water out and carry on with the project without having to start from scratch. they turned creative mode on for me so I could repair it, and then they just kind of left it on for me afterwards. since then I ’ve been using creative mode to make these puzzle challenges, like little constructed puzzles for people to solve, and I ’ve been putting them up on Facebook and sharing them around. it ’s turned Minecraft into this way of bringing people together, really, with these creative projects and challenges instead of just everyone playing separately.

% matched lemmas: big, build, huge, massive
\end{textsample}
