\begin{textsample}{NEG Dim 2 – unprofiled\_gpt – Score -3.00 – unprofiled\_gpt/t001107\_gpt.txt}  \label{ex:f2_neg_029}
We got in really late, and when we first came out of the metro the street just looked so rough, like it had been totally vandalised.
It felt a bit dodgy walking to the apartment at that time of night.
But then the next day, in the daylight, it actually looked really nice and totally different, which was a bit of a relief.
The thing with Barcelona is all the main sights are really spread out.
We ended up spending more time walking between places than actually seeing things.
We could ’ve done the tourist buses or figured out the public transport, but because it was such a short trip we just hadn't researched it properly.
Compared to Paris, where everything ’s really close together and you can just wander from one \textbf{big} sight to the next, it felt a bit annoying.
So we kind of just walked everywhere.
I didn't really mind, but the others aren't used to that much walking.
On the first day we just wandered around and stumbled on this festival, which was really nice.
Then in the evening we went to this \textbf{massive} light and fountain thing at what ’s now the national museum.
It looks like it used to be a palace or a stately home, up on a hill with all these fountains and beautiful steps, and at the bottom there ’s this \textbf{huge} fountain with music and a water display.
That was miles away as well, so more walking, and because I ’d vaguely suggested it I somehow ended up in charge of getting us there, even though I ’d never been before.

% matched lemmas: big, huge, massive
\end{textsample}
