\begin{textsample}{NEG Dim 2 – profiled\_gpt – Score -2.00 – profiled\_gpt/t000657\_gpt.txt}  \label{ex:f2_neg_015}
yeah so when I did go back on the server after that break I ’d had this idea in my head for ages about doing this absolutely \textbf{massive} tower, like really ambitious, just shooting up into the sky.
But then I started thinking it ’d be a bit boring if it was just me doing my own \textbf{big} solo thing again, so instead I started setting these little challenges for people, smaller projects that everyone could get involved in. we were working on one of those and we ’d got quite a lot of the structure done when this bloke who reckons he ’s an expert with TNT decided he was going to “ help ” with the digging. he blew out the walls a bit too enthusiastically and basically managed to flood the whole area we were working in. water everywhere, completely ruined what we ’d already \textbf{built}. so after that disaster I just said, look, can we go into creative mode for this bit so we can fix it properly and carry on. they switched creative on and we repaired all the damage and finished what we were doing. and then, because they kind of forgot to turn creative off for me afterwards, I ’ve just kept using it since. with creative mode still on I started putting together these little puzzle challenges, like self‑contained things people can try and solve.
I ’ve been taking screenshots and videos and sticking them up on Facebook, showing people what I ’ve \textbf{built} and inviting them to come on and have a go. it ’s turned into this way of using Minecraft less as just a game I play on my own and more as a way of bringing people together, getting friends involved in these creative projects and seeing what they come up with as well.

% matched lemmas: big, build, massive
\end{textsample}
