\begin{textsample}{POS Dim 5 – profiled\_gpt – Score 2.00 – profiled\_gpt/t001151\_gpt.txt}  \label{ex:f5_pos_005}
right so it ’s like this six‑day Montenegro thing and the itinerary is actually mad detailed yeah, like every \textbf{single} day is crammed. day one in the morning there ’s this orientation workshop, then something about the last three decades of Montenegro, then a recapitulation of the political situation and interethnic relations and all that. the grammar in this thing is actually \textbf{awful} though, like you can tell whoever wrote it didn't really proofread it properly, some of the sentences don't even make sense. then over the six days they ’ve got us going to all these different places – media places like TV or radio stations, then political institutions, so probably parliament or some government offices or whatever. they ’ve put in visits to religious sites as well, like churches or mosques, so it ’s all very “ understand the culture and history ” type stuff. there ’s schools on there too, so we ’re going to visit some local school, maybe meet students or teachers, that kind of exchange thing. and it ’s not just workshops and talks, there ’s excursions as well, so trips out to other towns or somewhere in the countryside, proper sightseeing built in. every day is like workshop in the morning, visit somewhere in the afternoon, then another activity, just constantly on the move. reading it out you can hear all the clunky English but you still get the idea – it ’s going to be really full‑on, loads of institutions, loads of learning, and barely any free time.

% matched lemmas: awful, single
\end{textsample}
