\begin{textsample}{POS Dim 2 – profiled\_gpt – Score 1.00 – profiled\_gpt/t000716\_gpt.txt}  \label{ex:f2_pos_013}
well of course while all this was going on you were out for ages, paying bills and doing bits and pieces, and you didn't get back, so I was just stuck there with all that shopping in the boot that really ought to have been in the fridge.
It was absolutely freezing as well, so I was thinking, oh for goodness ’ sake, this is just what I need, sitting here waiting and all the food in the car.
And then I ended up spending ages \textbf{chatting} with her – you know, my former student – and she is such a lovely girl, really funny and very talented.
She ’s running these big choirs now, performance and workshop choirs, and they train for about six weeks and then they put on these big shows twice a year.
It sounds marvellous what she ’s doing with them.
When she was a teenager in my theory lessons she used to have everybody in stitches, honestly, just uproarious laughter, the whole class.
But even with all that going on she still managed to get the whole lot of them through their exams.
That was the thing about her, she could clown around and make everyone laugh, but underneath it she was really capable and she worked hard enough to pull everyone along with her.
So I was quite happy standing there talking to her, even though I was stuck and the shopping was in the boot, because it was just so nice to see how she ’s turned out and hear about these choirs she ’s running now.

% matched lemmas: chat
\end{textsample}
