\begin{textsample}{POS Dim 4 – profiled\_gpt – Score 4.00 – profiled\_gpt/t000394\_gpt.txt}  \label{ex:f4_pos_007}
whether it ’s “ me ” or “ us ”, I don't think there ’s any point trying to pin blame on either of us.
You haven't done anything wrong, and I really don't want you sitting there \textbf{feeling} guilty or beating yourself up about it, because that ’s just not what this is about.
What ’s happened between us hasn't been about you doing some specific bad thing, or me doing some specific bad thing.
It ’s the \textbf{way} our characters have interacted over the last two years, the \textbf{way} we fit – or don't fit – together.
That ’s what ’s led us here, not some single action you should \textbf{feel} ashamed of or held responsible for.
I know you might not see it that \textbf{way}, but from my side I ’ve been absolutely eaten up by guilt about ending it.
I ’ve gone over and over it in my \textbf{head}, \textbf{feeling} awful about hurting you and about not being able to \textbf{make} it work.
So if anyone ’s been drowning in guilt, it ’s me.
And that ’s exactly why I ’m saying this : the whole guilt thing, for both of us, it just doesn't help.
It keeps us \textbf{stuck}.
If you ’re going to move on – and if I ’m going to move on – we both have to drop this idea that someone has to be “ at fault ”.
There doesn't have to be a villain here.
It ’s just the \textbf{way} things have turned out between two people over time, and the only \textbf{way} either of us gets any peace is by letting go of the guilt and that \textbf{way} of thinking.

% matched lemmas: feel, head, make, stick, way
\end{textsample}
