\begin{textsample}{POS Dim 4 – unprofiled\_gpt – Score 4.00 – unprofiled\_gpt/t001254\_gpt.txt}  \label{ex:f4_pos_027}
I do genuinely find that whole system really interesting, partly because it gives the director of studies such a \textbf{clear} window into what ’s going on in every classroom.
If all the teachers are using the same layout on the board, the same \textbf{way} of presenting vocabulary and aims, then when a student comes to complain about a particular teacher, the director actually has something concrete to go on.
They know what ’s supposed to be happening in every lesson, so they can say, “ Well, this is how it should look, ” and check whether that ’s happening or not.
Where they are, it was all put in place through negotiation with the permanent teachers, which \textbf{makes} sense if you ’re there all year and you ’ve got a stable staff. \textbf{Everyone} can sit down, talk it through, agree on where the vocabulary goes, what colours to use, all of that.
But at a summer school, that kind of process just isn't really possible.
People are in and out, it ’s short-term, and you don't have the luxury of weeks of discussion.
So I ’m thinking that if I do try to bring some of those ideas in, it ’ll have to be \textbf{more} of a top‑down thing : “ This is how we ’re doing it this summer. ” I ’m not entirely convinced the visiting staff from the London school will actually \textbf{stick} to it, though.
I can imagine them nodding and then just \textbf{carrying} on as they always have.

% matched lemmas: carry, clear, everyone, make, more, stick, way
\end{textsample}
